Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-28 draft.tex
stuff

>>>>

        On the one hand, given $x, y \in T$, 
        where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
            \left\| F_T(x) - F_T(y) \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
            \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
            \right\|_{2}
            \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
            2\sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
            \left\| x - y \right\|_{2}
        On the one hand, given $x, y \in T$, 
        where $\| x \|_{2} \leq \| y \|_{2}$ without loss of generality, we find 
            \left\| F_T(x) - F_T(y) \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y
            \right\|_{2}
                \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y
            \right\|_{2}
                \frac{ \| A_{T}^{-1} y \|_{1} }{ \|x\|_2 } y - \frac{ \| A_{T}^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
            \right\|_{2}
            \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
            \frac{\|y\|}{\|x\|}
            \|A_{T}^{-1} y\|_1 \|y\|_{2}
            \left| \frac{1}{\|x\|} - \frac{1}{\|y\|} \right|
            \frac{ \| A_{T}^{-1} x \|_{1} }{ \|x\|_2 } 
            \right\|_{2}
            \left| \|A_{T}^{-1} x\|_1 - \|A_{T}^{-1} y\|_1 \right|
            \frac{\|y\|}{\|x\|}
            \|A_{T}^{-1} y\|_1 \|y\|_{2}
            \left| \frac{ \|y\|_{2} - \|x\|_{2} }{\|x\|_{2} \|y\|_{2}} \right|
            3 \sqrt{n} \sigma_{\max}(A_{T}^{-1}) 
            \left\| x - y \right\|_{2}
        On the other hand, given $x, y \in F_T(T)$, 
        where $\| A_{T}^{-1} y \|_{1} \leq \| A_{T}^{-1} x \|_{1}$ without loss of generality, we find 
            \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
            \right\|_{2}
                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
            \right\|_{2}
                \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y
            \right\|_{2}
                \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A_{T}^{-1} y \|_{1} } y
            \right\|_{2}
            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{1} } 
            \right\|_{2}
            \left| \|x\|_2 - \|y\|_2 \right|
            \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{1} }
            \|y\|_2^{2}
            \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} \| A_{T}^{-1} y \|_{1} }
            \frac{ \|x\|_2 }{ \| A_{T}^{-1} x \|_{2} } 
            \right\|_{2}
            \left| \|x\|_2 - \|y\|_2 \right|
            \frac{ \|y\|_2 }{ \| A_{T}^{-1} x \|_{2} }
            \|y\|_2^{2}
            \frac{ \| A_{T}^{-1} y \|_{1} - \| A_{T}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{2} \| A_{T}^{-1} y \|_{2} }
            \left( 2 + \sqrt{n} \frac{\sigma_{\max}(A_{T}^{-1}) }{ \sigma_{\min}(A_{T}^{-1}) } \right) \sigma_{\min}(A_{T}^{-1})^{-1} 
            \left\| x - y \right\|_{2}
            \left( 2 + \sqrt{n} \kappa(A_{T}) \right) \sigma_{\max}(A_{T})
            \left\| x - y \right\|_{2}
        By convexity of the range of $F_T(T)$, 
        we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
        We recall that $\sigma_{\max}(A_{T}^{-1}) = \sigma_{\min}(A_{T})^{-1}$ and $\sigma_{\min}(A_{T}^{-1})^{-1} = \sigma_{\max}(A_{T})$.
